Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-13 latex/comp_or.tex
2 - abs(epsilon) removed

\begin{table}[H]
	\centering
	\caption{Performance for different number of concurrent processes with $1.2 \times volume$}  \label{tab:procs}
%	\footnotesize
	\scriptsize
	\begin{tabular}{c| c | c | c c c c c c c c }
	\toprule
	{\it Scenario} & $method$ &{\bf numProcs}    & \textbf{1} & \textbf{4} & \textbf{8} & \textbf{16} & \textbf{24} & \textbf{32} & \textbf{40} & \textbf{48}  \\
	\toprule
	\multirow{4}{*}{\it {1}}  &\multirow{2}{*}{\it {mpShims}}  &{\bf scores}      & 10909 & 10936 & 11022 & 11003 & 11033 & 11021 & 11013 & 11033 \\
	                          &                                &{\bf run-time (s)}& 0.12 & 0.23 & 0.44 & 0.65 & 1.13 & 1.74 & 2.32 & 3.68  \\
                              \cmidrule{2-11}
	                          &\multirow{2}{*}{\it {mpACO}}    &{\bf scores}               & 4 & 4 & 8 & 16 & 24 & 32&& \\
	                          &                                &{\bf run-time (s)}& 4 & 4 & 8 & 16 & 24 & 32&& \\
	\cmidrule{1-11}
	\multirow{4}{*}{\it {2}}  &\multirow{2}{*}{\it {mpShims}} &{\bf scores}       & 40016 & 40071 & 40071 & 40078 & 40078 & 40073 & 40083 & 40083 \\
	                          &                               &{\bf run-time (s)} & 2.72 & 2.85 & 2.15 & 1.95 & 3.10 & 20.32 & 13.95 & 17.24  \\
                              \cmidrule{2-11}
	                          &\multirow{2}{*}{\it {mpACO}}   &{\bf scores}       & 4 & 4 & 8 & 16 & 24 & 32&& \\
	                          &   &{\bf run-time (s)}         & 4 & 4 & 8 & 16 & 24 & 32&& \\				
	\bottomrule		
\end{tabular}

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data20.csv};

@@

		\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\end{center}
	\label{fig:mpShimsData20}
\end{figure}

Observing Figure \ref{fig:mpShimsData20}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

\begin{figure}[h!]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data50.csv};

@@

		\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\end{center}
	\label{fig:mpShimsData50}
\end{figure}

Observing Figure \ref{fig:mpShimsData50}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

\begin{figure}[h!]

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {Shims_p1data100.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				ylabel={\bf Scores},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {Shims_p2data100.csv};

@@

		\caption{{\it mpShims} performance with $2.0 \times volume$.}
	\end{center}
	\label{fig:mpShimsData100}
\end{figure}

Observing Figure \ref{fig:mpShimsData100}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is 8. For {\it Scenario 2}, the best number is 16.

>>>>

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data20.csv};

@@

	\end{center}
	\caption{ {\it mpShims} performance with $1.2 \times volume$. }
	\label{fig:mpShims2data20}
\end{figure}

Observing Figure \ref{fig:mpShims2data20}, it may be noticed that the best number of processes for {\it Scenario 1} (closest to the upper left corner) is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{4}.

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpShims2data50.csv};

@@

	\end{center}
	\caption{{\it mpShims} performance with $1.5 \times volume$.}
	\label{fig:mpShims2data50}
\end{figure}

Observing Figure \ref{fig:mpShims2data50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{8}.

\begin{figure}[H]

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO1data20.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO2data20.csv};

@@

	\end{center}
	\caption{{\it mpACO} performance with $1.2 \times volume$.}
	\label{fig:mpACO2data20}
\end{figure}

Observing Figure \ref{fig:mpACO2data20}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{40}. For {\it Scenario 2}, the best number is \textbf{1}.

\begin{figure}[H]

	\begin{center}
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 1 computation times (s)},
				ylabel={\bf Score},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO1data50.csv};

				\legend{\it parallel processes}
			\end{axis}
		\end{tikzpicture}%
		~%
		%
		\begin{tikzpicture}[scale=0.8, samples=100]
			\begin{axis}[
				myplotstyle,
				xlabel={\bf Scenario 2 computation times (s)},
				]
				\addplot+[
				only marks,	
				nodes near coords = {\numProcs{}},
				visualization depends on = {value \thisrow{np} \as \numProcs},						
				]
				table[x=time, y=score, col sep=comma] {mpACO2data50.csv};

	\end{center}
	\caption{{\it mpACO} performance with $1.5 \times volume$.}
	\label{fig:mpACO2data50}
\end{figure}

Observing Figure \ref{fig:mpACO2data50}, it may be noticed that the best number of processes for {\it Scenario 1} is \textbf{1}. For {\it Scenario 2}, the best number is \textbf{16}.
